\documentclass[a4paper]{article}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}

\title{Preliminary Design Document , Operating Systems}

\author{Nilesh Kulkarni(110050007), \\Rajlaxmi(110050087), \\Sushant Hiray(110050009), \\Deepali Adlakha(11d170020), \\Sanchit Garg(110050035), \\Vipul Harsh(110050034)}

\date{\today}

\begin{document}
\maketitle

\begin{abstract}
The aim of the project is to implement the undersaid things. Allocation of swap space to a process, loading of code of a process in its swap space, allocation of page frames to processes, loading of initial page(s) in memory, raising of page faults during operation of a process, etc.
\end{abstract}



\section{Tasks}


\subsection{Memory Management Unit}
 A Memory Management unit with the following functionalities.
    \begin{enumerate}
        \item Normal Page Table for translating Logical addresses to Physical addresses. 
        \item Raise Page fault interrupt and execute the VM routine for Page handling, in case of a missing Page table entry.
        \item Page Table Entry will encapsulate following attributes: valid bit, dirty bit, reference bit(s)(required for LRU), *\footnote{Things marked in asterisk would be implemented if time permits}sharing information(linked list of process).      
        \item Page Table will be stored in the OS's RAM 
        \item *Inverted Page Table
    \end{enumerate}
   
   
\subsection{Virtual Memory Manager}
   \begin{enumerate}
        \item Routine for Page fault Handling.
        \item Handling Protection Issues
        \item Process Creation: Copy on Write
        \item Preferred Page replacement Policies : LRU using local replacement and global replacement.
        \item *Implementing Working set for a process, along with promotion \& demotion (initial allocation taken from config file)
        
   \end{enumerate}
  
\subsection{Shared Memory Management}
    \begin{enumerate}
        \item Allow Process to share pages among them.
        \item Will especially come into play when process will Fork
        \item Will be signalled by MMU if a particular shared page is written by a process, so that copy on write can be implemented.
        
    \end{enumerate}
    
\subsection{Swap Space Manager}
    \begin{enumerate}
        \item Keeping track of Swap Space
        \item Support Page In \& Page Out functionality 
        \item Process swaped in \& swapped out when given calls by Medium Term Scheduler
        \item Pages swapped in and swapped out when asked by the VM Manager
        
    \end{enumerate}
    
    
\subsection{Medium Term Scheduler}
    \begin{enumerate}
        \item Perform Swap in and Swap out of a process, blocked or dormant                 \item Signal swap space manager to swap in \& swap out a Process 
    \end{enumerate}

\section{Handling Events}
    
    
    \subsection{Page Fault Event}
        \begin{enumerate}
            \item Block the faulting process \& estimate the time for page fault and create an interrupt accordingly to make the process "Ready". 
            \item MMU will signal the VM 
            \item VM will look up the replacement policy offered by the OS
            \item Depending on whether the allocation strategy is global or local, it will iterate over all the page tables and get the page to be replaced .
            \item The page should be swapped in, and the required page(which caused the page fault) to be swapped out.
            \item Update page table entries accordingly( processes to be kept in mind)
        \end{enumerate}
     \subsection{Protection Violation}
        \begin{enumerate}
            \item MMU will signal the VM 
            \item Process will be abort immediately on a violation of memory access
        \end{enumerate}
        
     \subsection{*Writing on Shared Memory}
        \begin{enumerate}
            \item Create a copy of the page that was shared, and make the process that wants to write to point to it.
            \item Update Page Table
            
         \end{enumerate}
  



\section{Deadline}
    Expected to be completed by 15th April. Incase the Design is too ambitious please suggest.
    
\end{document}
